---
title: "Cattle Movement Model"
author: "Dave Swain"
date: "07/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Cattle Behavioural Movement Model

This project aims to develop a cattle movement model that can be used to explore how behavioural drivers impact landscape use by cattle. As an agent based simulation model it uses a standard time step and a series of location based reference points that are used to determine the move. Individual moves are dealt with via a probabalistic model and the behavioural states determines the relative weighting. The cattle change between behavioural states based on a hierarchy of needs, again the change occurs in a probabalistic manner. The relative weighting of the shift between behavioural states is determined by a series of rules. These rules relate to a number of key drivers. The drivers include need for water, food, protection, reproductive state, general preferences and class of animal.

The location references points are food (local small scale and large scale landscape), water locations, middle of herd and individual.

```{r echo=FALSE}
library(geosphere)
library(ggplot2)
cattlepos <- data.frame(matrix(ncol=3, nrow=10))

colnames(cattlepos) <- c("ID", "x", "y")

cattlepos$ID <- c(1:10)



cattlepos$x <- floor(runif(10, 40, 60))
cattlepos$y <- floor(runif(10, 40, 60))


cenx <- floor(sum(cattlepos$x)/length(cattlepos$x))

ceny <- floor(sum(cattlepos$y)/length(cattlepos$y))


cattlepos$diffx <- cattlepos$x-cenx
cattlepos$diffy <- cattlepos$y-ceny

cattlepos$angle <- atan(cattlepos$diffy/cattlepos$diffx)

cattlepos$angle2 <- 2*pi - ((cattlepos$angle^2)^0.5)


#plot(cattlepos$x, cattlepos$y)

ggplot(cattlepos, aes(x,y)) + geom_point() + geom_text(aes(label=ID), vjust =2) +
  geom_point(aes(x=cenx, y=ceny), colour="blue", size = 10)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}

```

